---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753FALLshaw0050)
knitr::opts_chunk$set(echo = TRUE, fig.width = 6 )

```



# Functions
```{r}
library(Intro2R)
par(mar = c(15, 15, 15, 1)) 
```


## myboot2.R
This function takes in a iter number of iter, a vector, string of what label should be, the alpha, and the cx returns a hisogram of Bootstrap sample statistics

```{r}
myboot2(iter=10000,c(1,1,1,2,2,2,2,3,3,3,4,4),fun="mean",alpha=0.05,cx=1.5)
```



## myncurve.R
This function takes in the mean, standard deviation, and a lower tail probability starting point and returns a lower tail
```{r}
myncurve(mu=7,sigma=4,a=5)
```


## mysample.R
This function takes in sample size, iteration number and when to release table and returns a barplot
```{r}
mysample(10,.05)
```


## myzfunction.R
This function takes in a quantitative vector of data and returns a list containing the z value
```{r}
myzfunction(1:6)
```

## mymlnorm.R
This function takes in a sample vector, mean, sigma and returns 3D graph
```{r}
y = c(10,12,13,15,12,11,10)
mymlnorm(x=y,mu=seq(10,15,length=1000),sig=seq(0.1,3.5,length=1000),lwd=2,labcex=1)
```

# Getting an error for figure margin too large

## ntickets.R
This function takes in N Number of seats in the flight the probability a plane is truly overbooked and the probability of a "show" and returns 2 plots of Objective function Vs n and list containing nd, nc, N, p and gamma are outputed

```{r}
#ntickets(N=20, gamma = 0.02, p=0.95)
```

## mycltp.R
This function take in a sample size, number of iterations, rate of parameter and returns a histogram of sample mean, barplot of sample y, and probability function for poisson 

```{r}
#mycltp(2,10000,10)
```
